---
title: 'Supplemental Materials. Deliberative Reasoning Within the Machine: Can Large Language Models Reason Deliberatively?'
author: "Francesco Veri, Gustavo Umbelino, Nardine Alnemr"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2: default
  html_document: default
  pdf_document: default
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# install deliberr if the package doesn't exist
# renv::install("gumbelino/deliberr")

library(deliberr)
library(readr)
library(readxl)
library(dplyr)
library(rstatix)
library(tidyr)
library(ggplot2)
library(psych)
library(gridExtra)
library(ggpubr)
library(lme4)
library(emmeans)
library(car)
library(reshape2)

SURVEY_FILE <- "data/surveys.xlsx"
LLMS_FILE <- "data/llms_v2.csv"
CASES_FILE <- "data/cc_cases.csv"
PROMPTS_FILE <- "data/prompts.csv"
OUTPUT_DIR <- "data"

```

# Large-Language Models (LLMs)

```{r models, warning=FALSE}

# get models info
models <- read_csv(LLMS_FILE, show_col_types = FALSE) %>%
  filter(included) # only included "included" models]

models %>%
  group_by(provider, name) %>%
  summarise() %>%
  knitr::kable(caption = "LLMs", row.names = TRUE)

```

Building on our previous analysis, we selected models based on their performance. We chose 4 top[^1], which were consistently more consistent than chance, and 4 bottom models, which were consistently less consistent than chance in terms of deliberative reasoning.

[^1]: Note that `gemini-2.5-pro-preview-03-25` was replaced by `gemini-2.5-pro`, however, this version of the model became significantly slower and more expensive, since it has "thinking" enabled by default and cannot be toggled. As a result, we decided to use the *flash* version (`gemini-2.5-flash`), a lighter and cheaper alternative.

```{r cases_all, warning=FALSE, include=FALSE}

cc_cases <- read_csv(CASES_FILE, show_col_types = FALSE)

cc_cases %>% arrange(survey) %>%
  knitr::kable(caption = "Climate Cases", row.names = TRUE)

```

```{r surveys_all, warning=FALSE, include=FALSE}

# get deliberative survey names
survey_names <- unique(cc_cases$survey)

get_surveys <- function(survey_names) {
  
  surveys <- list()
  
  # Iterate over each sheet in the workbook
  for (survey_name in survey_names) {

    # Read the current sheet into a data frame
    df <- read_excel(SURVEY_FILE, sheet = survey_name)
    
    # Check if required columns exist
    required_columns <- c("considerations", "policies", "scale_max", "q-method")
    missing_cols <- setdiff(required_columns, colnames(df))
    if (length(missing_cols) > 0) {
      cat(
        "Sheet",
        survey_name,
        "is missing the following columns:",
        paste(missing_cols, collapse = ", "),
        "\n\n"
      )
      next
    }
    
    # Calculate the number of non-NA rows in "considerations" column
    n_c <- sum(!is.na(df$considerations))
    
    # Calculate the number of non-NA rows in "policies" column
    n_p <- sum(!is.na(df$policies))
    
    # Extract integer values from "scale_max" column, assuming they are already integers
    scale_max <- as.integer(na.omit(df$scale_max))
    
    # Extract logical (boolean) values from "q-method" column
    q_method <- as.logical(na.omit(df$`q-method`))
    
    surveys[[length(surveys) + 1]] <- tibble(
      survey = survey_name,
      considerations = n_c,
      policies = n_p,
      scale_max,
      q_method,
    )
    
  }
  
  surveys <- bind_rows(surveys)
  surveys
  
}

surveys <- get_surveys(survey_names)

surveys %>% arrange(survey) %>%
  knitr::kable(caption = "Surveys", row.names = TRUE)

```

```{r prompts_all, warning=FALSE, include=FALSE}

prompts <- read_csv(PROMPTS_FILE, show_col_types = FALSE)

prompts %>% 
  group_by(type) %>%
  summarise(n = n(), .groups = "drop") %>%
  knitr::kable(caption = "Number of Prompts by Type")

prompts %>% arrange(type) %>%
  select(-article) %>%
  knitr::kable(caption = "System Prompts", row.names = TRUE)

```

```{r format LLM data, include=FALSE}

llm_data <- read_csv("data/llm_data_clean.csv", show_col_types = FALSE)

llm_data_v2 <- read_csv("data/llm_data_v2_clean.csv", show_col_types = FALSE) %>%
  rename("prompt_uid" = "role_uid", "cuid" = "uuid")

llm_data <- bind_rows(llm_data, llm_data_v2)

# change temperature to -1 if NA
# this makes it easier to plot 
llm_data <- llm_data %>%
  mutate(temperature = ifelse(is.na(temperature), -1, temperature))

# fix models' names
llm_data <- models %>%
  select(model, name) %>%
  left_join(llm_data, join_by(model)) 

# replace model id with model name 
llm_data <- llm_data %>%
  mutate(model = name)

write_csv(llm_data, "data/llm_data_v2_clean_full.csv")

```

# Roles

```{r roles}

cc_roles <- read_csv("data/cc_roles.csv", show_col_types = F)

cc_roles %>%
  knitr::kable(caption = "Roles", row.names = TRUE)

```

```{r}

cc_llm_data <- llm_data %>%
  filter(survey %in% cc_cases$survey, prompt_uid %in% cc_roles$uid)

```

# Methods

## Data collection

We collected `r nrow(cc_llm_data)` responses generated by `r length(unique(models$name))` models cross `r length(cc_cases$survey)` surveys and `r nrow(cc_roles)` roles described above. We prompted each LLM 5 times with the same prompt. When available, we generated data varying `temperature` and `reasoning_effort` parameters. We set `temperature` to 0 (min) and 2 (max) while keeping the reasoning parameters unchanged. We also set the `reasoning_effort` to `low` while keeping the temperature unchanged.

We generated the data using either OpenRouter's API or the models' official API in different parts of the analysis. The original data generation (v1) was done using the official APIs and the latter (v2) was done using OpenRouter's API. We opted to use OpenRouter to overcome the need to manually write and update the code to communicate with different providers' APIs (e.g., OpenAI, Anthropic). We used the R package `deliberr` to generate data using the OpenReouter API.

### System prompt (Roles)

We instructed LLMs to play each of the roles described above by including a system instruction in each request following the pattern:

> *Answer the following prompts as **[article] [role]**, who **[description]**.*

For example:

> *Answer the following prompts as **`r cc_roles[12,]$article` `r cc_roles[12,]$role`**, who **`r cc_roles[12,]$description`**.*

## Analysis

We calculated one DRI value per model/survey/role/temperature/reasoning_effort by treating each LLM response as one participant in a deliberation. The role "all" indicates that all roles were part of that deliberation (n = 60 participants, which equals 5 participants for each of the 12 roles).


```{r, include=FALSE}
res <- list()
plots <- list()

for (model in unique(models$name)) {
  for (survey in cc_cases$survey) {
    for (temp in c(0, 2, -1)) {
      for (role in cc_roles$uid) {
        data <- llm_data %>%
          filter(model == !!model,
                 survey == !!survey,
                 prompt_uid == role,
                 temperature == temp) %>%
          mutate(pnum = row_number()) # treat each response as a participant
        
        if (nrow(data) < 5)
          next
        
        ic <- get_dri_ic(data)
        dri <- get_dri(ic)
        alpha <- get_dri_alpha(data)
        
        # split temperature and reasoning into 2 variables
        if (temp < 0) {
          r <- T
        } else {
          r <- F
        }
        
        res[[length(res) + 1]] <- tibble(model,
                                         survey, 
                                         role, 
                                         temperature = temp,
                                         reasoning_on = r,
                                         dri, 
                                         alpha, 
                                         n = nrow(data))
        
      }
      
    }
    
  }
  
}

res <- bind_rows(res)

# save temperature as NA if reasoning_effort is used
res %>%
  mutate(temperature = ifelse(temperature < 0, 
                              NA, temperature)) %>%
write_csv("data/dri_alpha_data.csv")
dri_alpha_data <- res

# this shows which models have which variations
dri_alpha_data %>%
  group_by(model) %>%
  summarise(n = n()) %>%
  arrange(n)

```

# Hypotheses Testing

## H1: Random Data

```{r}
random_res <- list()
N <- 5

set.seed(14)

## generate random data
survey_names <- res %>%
  select(survey) %>%
  unique()

relevant_surveys <- surveys %>%
  filter(survey %in% survey_names$survey)

for (i in 1:nrow(relevant_surveys)) {
  
  # get survey meta data
  survey <- relevant_surveys[i, ]$survey
  scale_max <- relevant_surveys[i, ]$scale_max
  c_n <- relevant_surveys[i, ]$considerations
  p_n <- relevant_surveys[i, ]$policies
  
  # generate N responses for each role
  for (j in 1:nrow(cc_roles)) {
    
    # get role
    role <- cc_roles[j,]$uid
    
    for (pnum in 1:N) {
      
      ## generate random Cs
      random_c <- sample(1:scale_max, size = c_n, replace = TRUE)
      padded_c <- c(random_c, rep(NA, 50 - c_n))
      c_df <- matrix(padded_c, nrow = 1, ncol = 50)
      colnames(c_df) <- paste0("C", 1:50)
      c_df <- as.data.frame(c_df)
      
      ## generate random Ps
      random_p <- sample(1:p_n, size = p_n, replace = FALSE)
      padded_p <- c(random_p, rep(NA, 10 - p_n))
      p_df <- matrix(padded_p, nrow = 1, ncol = 10)
      colnames(p_df) <- paste0("P", 1:10)
      p_df <- as.data.frame(p_df)
    
      # merge results
      random_res[[length(random_res)+1]] <- tibble(
        pnum,
        survey,
        role,
        c_df,
        p_df
      )
      
    }
  
  }

}

random_res <- bind_rows(random_res)

random_data <- random_res %>%
  group_by(survey, role) %>%
  summarise(n = n(), .groups = "drop")

random_dri <- list()

## calculate DRI for random participants
for (i in 1:nrow(random_data)) {
  role <- random_data[i,]$role
  survey <- random_data[i,]$survey
  
  # get subset of data to test
  random_dri_data <- random_res %>%
    filter(role == !!role, 
           survey == !!survey)
  
  # calculate dri
  ic <- get_dri_ic(random_dri_data)
  dri <- get_dri(ic)
  
  random_dri[[length(random_dri)+1]] <- tibble(
    random_data[i,],
    dri
  )
  
}

random_dri <- bind_rows(random_dri)

# select model/surveys
llm_data_it <- res %>%
  select(model, survey, temperature) %>%
  unique()

random_res <- list()

# test each model/survey
for (i in 1:nrow(llm_data_it)) {
  model <- llm_data_it[i,]$model
  survey <- llm_data_it[i,]$survey
  temperature <- llm_data_it[i,]$temperature
  
  # get subset of data to test
  test_data <- res %>%
    filter(model == !!model, 
           survey == !!survey,
           temperature == !!temperature,
           role != "all")
  
  if (nrow(test_data) < 12) next
  
  random_data <- random_dri %>%
    filter(model == !!model, 
           survey == !!survey)

  # compare model/survey DRI across roles
  test_result_ts <- wilcox.test(test_data$dri, random_data$dri)
  test_result_gt <- wilcox.test(test_data$dri, random_data$dri, alternative = "greater")
  
  # save response
  random_res[[length(random_res)+1]] <- tibble(
    model,
    survey,
    temperature,
    obs_mean = mean(test_data$dri),
    llm_N = nrow(test_data),
    random_mean = mean(random_data$dri),
    random_N = nrow(random_data),
    p_value_two.sided = test_result_ts$p.value,
    sig_two.sided = case_when(
      test_result_ts$p.value < 0.05 ~ "*",
      .default = "n.s."
    ),
    p_value_greater = test_result_gt$p.value,
    sig_greater = case_when(
      test_result_gt$p.value < 0.05 ~ "*",
      .default = "n.s."
    ),
  )
  
}

random_res <- bind_rows(random_res)

write_csv(random_res, "data/H1a_random_results.csv")
```


```{r, fig.width=14, fig.height=12}
# Read your file (adjust path if needed)
h1 <- random_res

# Optional: make shorter, nicer labels for models
h1 <- h1 |>
  left_join(models %>% 
              select(model), 
            join_by(model)) %>%
  mutate(model_clean = model)


# 2. Order models by average observed DRI ----------------------------------

model_order <- h1 |>
  group_by(model_clean) |>
  summarise(avg_obs = mean(obs_mean, na.rm = TRUE)) |>
  arrange(avg_obs) |>
  pull(model_clean)

h1 <- h1 |>
  mutate(model_clean = factor(model_clean, levels = model_order),
         sig = p_value_greater < 0.05)

# 3. Long format: observed vs random ---------------------------------------

h1_long <- h1 |>
  select(model_clean, survey, temperature, obs_mean, random_mean, sig) |>
  mutate(temperature = case_when(
    temperature == -1 ~ "Reasoning ON, default temperature",
    temperature == 0 ~ "Temperature = 0, reasoning OFF",
    temperature == 2 ~ "Temperature = 2, reasoning OFF"
  )) |>
  pivot_longer(
    cols = c(obs_mean, random_mean),
    names_to = "type",
    values_to = "mean_dri"
  ) |>
  mutate(
    type = dplyr::recode(type,
                  "obs_mean" = "Observed DRI",
                  "random_mean" = "Random baseline")
  )


ph1 <- h1_long %>%
  ggplot(aes(x = model_clean, y = mean_dri, group = model_clean)) +
  
  # grey connector between random and observed
  geom_line(color = "grey70", linewidth = 0.6) +
  
  # RANDOM baseline → solid purple
  geom_point(
    data = subset(h1_long, type == "Random baseline"),
    color = "#7570b3",
    size = 3
  ) +
  
  # OBSERVED not significant → empty green circle
  geom_point(
    data = subset(h1_long, type == "Observed DRI" & sig == FALSE),
    shape = 21,
    fill  = "white",
    color = "#1b9e77",
    stroke = 1.2,
    size = 3
  ) +
  
  # OBSERVED significant → filled green circle
  geom_point(
    data = subset(h1_long, type == "Observed DRI" & sig == TRUE),
    shape = 21,
    fill  = "#1b9e77",
    color = "#1b9e77",
    size = 3
  ) +
  
  facet_wrap( ~ temperature + survey, nrow = 3, ncol = 3) +
  
  # scale_shape_manual(
  #   name = "Observed > random (p < .05)",
  #   values = c(`TRUE` = 16, `FALSE` = 1),  # TRUE = filled, FALSE = hollow
  #   labels = c("No", "Yes")
  # ) + # FIXME
  
  labs(
    title    = "H1: Within-model coherence in DRI",
    subtitle = "Observed DRI relative to random baseline",
    x = "Model",
    y = "Mean DRI"
  ) +
  
  theme_minimal(base_size = 20) +
  
  theme(
    axis.text=element_text(size=12),
    axis.title=element_text(size=14,face="bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    legend.position = "bottom"
  ) 
  

ph1

ggsave("plots/Fig1.png", ph1, width = 12, height = 12, dpi = 300)


```

# Other analyses

```{r, include=FALSE}
library(lme4)
library(lmerTest)
library(emmeans)
library(broom.mixed)
library(patchwork)

# =========================
# 1. LOAD DATA
# =========================
df <- read.csv("data/dri_alpha_data.csv", stringsAsFactors = FALSE)

# =========================
# 2. CLEANING
# =========================
df <- df %>%
  mutate(
    model = factor(model),
    survey = factor(survey),
    role = factor(role),
    dri = as.numeric(dri),
    temperature = suppressWarnings(as.numeric(temperature)),
    reasoner = as.character(reasoning_on),
    reasoner_n = case_when(
      reasoner %in% c("1", "TRUE", "true", "yes", "Yes") ~ 1,
      reasoner %in% c("0", "FALSE", "false", "no", "No") ~ 0,
      TRUE ~ suppressWarnings(as.numeric(reasoner))
    )
  )
```


```{r}
# =========================
# 3. CREATE ANALYSIS VARIABLES
# =========================

# H2: model configuration = model + operational condition
df_h2 <- df %>%
  mutate(
    condition = case_when(
      !is.na(temperature) ~ paste0("temp = ", temperature),
      is.na(temperature) & !is.na(reasoner_n) ~ paste0("reasoner = ", reasoner_n),
      TRUE ~ "default"
    ),
    model_configuration = paste(model, "|", condition),
    model_configuration = factor(model_configuration)
  )

# H3: only cases where temperature is observed
df_h3 <- df %>%
  filter(!is.na(dri), !is.na(temperature)) %>%
  mutate(
    model = factor(model),
    survey = factor(survey),
    temperature = factor(temperature)
  )

# H4: only models where reasoning can be toggled on/off
reasoning_capable_models <- df %>%
  group_by(model) %>%
  summarise(n_modes = n_distinct(reasoner_n, na.rm = TRUE), .groups = "drop") %>%
  filter(n_modes > 1) %>%
  pull(model)

df_h4 <- df %>%
  filter(model %in% reasoning_capable_models, !is.na(dri), !is.na(reasoner_n)) %>%
  mutate(
    model = factor(model),
    survey = factor(survey),
    reasoner_n = factor(reasoner_n, levels = c(0, 1))
  )

cat("\n=========================\n")
cat("DATA OVERVIEW\n")
cat("=========================\n")
cat("Full data rows: ", nrow(df), "\n")
cat("H2 rows: ", nrow(df_h2), "\n")
cat("H3 rows: ", nrow(df_h3), "\n")
cat("H4 rows: ", nrow(df_h4), "\n\n")
```


```{r}
# =========================
# 4. COMMON THEME
# =========================
theme_paper <- theme_minimal(base_size = 13) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(linewidth = 0.3, color = "grey85"),
    axis.title = element_text(face = "bold"),
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "grey30")
  )

dir.create("figures", showWarnings = FALSE)
```

## H2: Model Configuration Effect
```{r}

# Null model
m_h2_null <- lmer(
  dri ~ (1 | role) + (1 | survey),
  data = df_h2,
  REML = FALSE
)

# Full model
m_h2 <- lmer(
  dri ~ model_configuration + (1 | role) + (1 | survey),
  data = df_h2,
  REML = FALSE
)

cat("\n=========================\n")
cat("H2: MODEL CONFIGURATION EFFECT\n")
cat("=========================\n")
print(summary(m_h2))
print(anova(m_h2))
print(anova(m_h2_null, m_h2))

# Estimated marginal means
emm_h2 <- emmeans(m_h2, ~ model_configuration)
emm_h2_df <- as.data.frame(emm_h2)

p_h2 <- ggplot(
  emm_h2_df,
  aes(x = reorder(model_configuration, emmean), y = emmean, fill = emmean)
) +
  geom_col(width = 0.75, color = "grey20") +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.15,
    linewidth = 0.7
  ) +
  coord_flip() +
  scale_fill_gradient2(
    low = "#d73027",
    mid = "#fee08b",
    high = "#1a9850",
    midpoint = mean(emm_h2_df$emmean, na.rm = TRUE),
    name = "Predicted\nDRI"
  ) +
  labs(
    x = "Model configuration",
    y = "Estimated DRI",
    title = "H2: Deliberative Reason Index across model configurations",
    subtitle = "Mixed-effects model controlling for role and survey"
  ) +
  theme_paper +
  theme(
    panel.grid.major.y = element_blank(),
    legend.position = "right"
  )
p_h2
ggsave("figures/h2_model_configuration.png", p_h2, width = 11, height = 8, dpi = 300)
```

## H3: Temperature Effect
```{r}

m_h3 <- lmer(
  dri ~ temperature + (1 | model) + (1 | survey),
  data = df_h3
)

cat("\n=========================\n")
cat("H3: TEMPERATURE EFFECT\n")
cat("=========================\n")
print(summary(m_h3))
print(anova(m_h3))

# coefficient dataframe
coef_h3_df <- broom.mixed::tidy(
  m_h3,
  effects = "fixed",
  conf.int = TRUE
) %>%
  filter(term != "(Intercept)") %>%
  mutate(term_label = "Temperature 0/2")
```

## H4: Reasoning Effect
```{r}

m_h4 <- lmer(
  dri ~ reasoner_n + (1 | model) + (1 | survey),
  data = df_h4
)

cat("\n=========================\n")
cat("H4: REASONING EFFECT\n")
cat("=========================\n")
print(summary(m_h4))
print(anova(m_h4))

coef_h4_df <- broom.mixed::tidy(
  m_h4,
  effects = "fixed",
  conf.int = TRUE
) %>%
  filter(term != "(Intercept)") %>%
  mutate(term_label = "Reasoning OFF/ON")
```


```{r}
# =========================
# 8. SHARED COEFFICIENT AXIS FOR H3/H4
# =========================

xmin <- min(coef_h3_df$conf.low, coef_h4_df$conf.low, na.rm = TRUE)
xmax <- max(coef_h3_df$conf.high, coef_h4_df$conf.high, na.rm = TRUE)
x_limits <- c(xmin, xmax)

# -------------------------
# H3 coefficient plot
# -------------------------
p_h3_coef <- ggplot(coef_h3_df, aes(x = estimate, y = term_label)) +
  geom_vline(
    xintercept = 0,
    linetype = "dotted",
    color = "red3",
    linewidth = 1.2
  ) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.15, linewidth = 1) +
  geom_point(size = 3) +
  coord_cartesian(xlim = x_limits) +
  labs(
    x = "Coefficient estimate",
    y = NULL,
    title = "H3: Temperature effect",
    subtitle = "Mixed-model estimate with 95% CI"
  ) +
  theme_paper +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_blank()
  )
```


```{r}
# -------------------------
# H4 coefficient plot
# -------------------------
p_h4_coef <- ggplot(coef_h4_df, aes(x = estimate, y = term_label)) +
  geom_vline(
    xintercept = 0,
    linetype = "dotted",
    color = "red3",
    linewidth = 1.2
  ) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.15, linewidth = 1) +
  geom_point(size = 3) +
  coord_cartesian(xlim = x_limits) +
  labs(
    x = "Coefficient estimate",
    y = NULL,
    title = "H4: Reasoner effect",
    subtitle = "Mixed-model estimate with 95% CI"
  ) +
  theme_paper +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_blank()
  )

p_h3_h4 <- p_h3_coef / p_h4_coef
p_h3_h4
ggsave("figures/h3_h4_coefficients.png", p_h3_h4, width = 10, height = 8, dpi = 300)
```


```{r}
# =========================
# WITHIN-MODEL SLOPE PLOTS
# =========================

# H3 slope plot
df_h3_plot <- df_h3 %>%
  group_by(model, temperature) %>%
  summarise(mean_dri = mean(dri, na.rm = TRUE), .groups = "drop")

p_h3_slope <- ggplot(
  df_h3_plot,
  aes(x = temperature, y = mean_dri, group = model, color = model)
) +
  geom_line(linewidth = 1, alpha = 0.8) +
  geom_point(size = 3) +
  labs(
    x = "Temperature",
    y = "Mean DRI",
    title = "Within-model change",
    subtitle = "Average DRI by temperature"
  ) +
  theme_paper

# H4 slope plot
df_h4_plot <- df_h4 %>%
  group_by(model, reasoner_n) %>%
  summarise(mean_dri = mean(dri, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    reasoner_n = factor(reasoner_n, levels = c(0, 1),
                        labels = c("Reasoning OFF", "Reasoning ON"))
  )

p_h4_slope <- ggplot(
  df_h4_plot,
  aes(x = reasoner_n, y = mean_dri, group = model, color = model)
) +
  geom_line(linewidth = 1, alpha = 0.8) +
  geom_point(size = 3) +
  labs(
    x = NULL,
    y = "Mean DRI",
    title = "Within-model change",
    subtitle = "Average DRI by reasoning mode"
  ) +
  theme_paper
p_h4_slope
p_h3_slope

(p_h4_coef/p_h4_slope)
((p_h3_coef/p_h3_slope))
ggsave("figures/h3_temperature_slope.png", p_h3_slope, width = 8, height = 5, dpi = 300)
ggsave("figures/h4_reasoner_slope.png", p_h4_slope, width = 8, height = 5, dpi = 300)

```

